---
title: "PCA_Analysis_1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("corrplot")
library("ggplot2")
library("dplyr")
library("psych")
```

```{r setting values, include = FALSE}
df = msq
df = select(df,Extraversion, Neuroticism, active:scornful)
df = df[,colSums(is.na(df))<400]
df =  df[(rowSums(is.na(df))==0),]


features = select(df, -Extraversion, -Neuroticism)
PCAdata = prcomp(features, scale=TRUE)

top5 = PCAdata$rotation[,1:5]
```

### My read on the first 6 PCAs
1. PC1: energetic happiness
1. PC2: inverse unhappiness
1. PC3: disquiet/unsettled (reversed serenity)
1. PC4: I'm not tired
1. PC5: "I'm not angry!" (while *cough* "frustrated")

```{r Top 5 PCAs, echo=FALSE}
corrplot(top5, is.corr=FALSE)
```

<center>Eigenvalues $\lambda$</center>
$$
Proportion \ variance \ explained \ by \ \lambda_1 = \dfrac{\lambda_1}{\sum(\lambda_n)}
$$

```{r Plot of eigenvalues, echo = TRUE}
qplot(,PCAdata$sdev)
#This is a plot of the eigenvalues by the PCA number
```

General pattern: Early PCAs are determined by a mix of weak influences from multiple associated variables.

The first few could be captured by fairly distinct concepts.

Middle PCAs are often 1 strong influence and many weak ones, harder to pinpoint to a phrase. Mudddled.

Late PCAs are strongly determined (functionally defined as) 1 or 2 variables.